Minimax lower bounds for source localization

### 2017-01-22 paper.tex
Remove section on Holder continuity.

\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}

We can trivially expand the domain of impulse responses to which the lower
bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
continuous functions. These are functions which satisfy
\begin{equation}
	\abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
\end{equation}
for some constant $\kappa$, and for $\alpha > 0$. Using this property,
equation~\eqref{eq:delta-bound} reads
\begin{equation} \label{eq:holder-delta-bound}
	\norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
\end{equation}
Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
w})^{1/2\alpha}$, to procure an asymptotic lower bound
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
w}\bigg)^{1/\alpha}.
\end{equation}

>>>>

%\subsection{From Lipschitz to $\alpha$-Holder continuous impulse responses}

%We can trivially expand the domain of impulse responses to which the lower
%bound in~\eqref{eq:main-lower-bound} applies to include $\alpha$-Holder
%continuous functions. These are functions which satisfy
%\begin{equation}
%    \abs{g(u) - g(v)} \leq \kappa \abs{u - v}^\alpha \, \forall \, u, v \in \text{dom} \; g
%\end{equation}
%for some constant $\kappa$, and for $\alpha > 0$. Using this property,
%equation~\eqref{eq:delta-bound} reads
%\begin{equation} \label{eq:holder-delta-bound}
%    \norm{\v\Delta}^2 \leq \kappa^2 (2 \delta)^{2\alpha} \bigg(\frac{(w + 2\delta) m}{S} + 1\bigg).
%\end{equation}
%Hence, we choose $\delta = (\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
%w})^{1/2\alpha}$, to procure an asymptotic lower bound
%\begin{equation}
%    \mathfrak{M}_n(\mathcal{P}, \Phiorho) \geq \frac{1}{4} \bigg(\frac{\sigma^2 S}{2^{2\alpha + 1} nm \kappa^2
%w}\bigg)^{1/\alpha}.
%\end{equation}
